### 2023-06-19 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
adding in velocity result within lubrication layer

%In the single-component runs, ... In the multicomponent runs, we see that phase separation does not occur in the channel. When it does occur, we see spikes in the bending and tension energies. \todo[inline]{Discussion of what we see}

@@

>>>>

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the soild wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall.

Using the definition of the lubrcication layer outlined in Section ???,
fit the horizontal flow profile to a quadratic function and plot the
coefficients of the Poisseuille and linear shear in Figure~\ref{}. We
only consider cases where the vesicle has reached a steady shape is only
under going tank treading. We observe that the Poisseuille coefficient
can be either positive or negative, meaning that the pressure in the
lubcrication layer switches signs. This behavior is caused when the
tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
=\sigma_s$ which is the usual Marangoni effect.

\begin{figure}
%  \begin{minipage}{0.99\columnwidth}
    \centering
    \subfigimg[width=\columnwidth]{(a)}{figures/SC_top.pdf}
    \subfigimg[width=\columnwidth]{(b)}{figures/SC_bot.pdf}
    \subfigimg[width=\columnwidth]{(a)}{figures/SCp55_top.pdf}
    \subfigimg[width=\columnwidth]{(b)}{figures/SCp55_bot.pdf}
    \subfigimg[width=\columnwidth]{(a)}{figures/MCp5_top.pdf}
    \subfigimg[width=\columnwidth]{(b)}{figures/MCp5_bot.pdf}
%  \end{minipage}
%  \hfill
%  \begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
%    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
%    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
%  \end{minipage}
%  \caption{\label{fig:Energy} \small The Bending (blue), tension
%  (yellow), and phase (red) energies for a (a/b) single-component
%  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
%  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
%  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
\end{figure}
